Measurement and Probability in Fuzzy Quantum Theories

### 2017-02-15 prop_iop.tex
prop_iop.tex \section{Examples for Quantum Interval-valued Probability Measures\label{sec:Examples-for-QuantumIVPM}} Added...

\documentclass[12pt]{iopart}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{iopams}
\usepackage{setstack}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage{}%
\begin{comment}
 \bibliographystyle{plain}
\bibliography{prop}

>>>>

\documentclass[12pt]{iopart}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{iopams}
\usepackage{setstack}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Examples for Quantum Interval-valued Probability Measures\label{sec:Examples-for-QuantumIVPM}}

\begin{example}[Three-dimensional quantum three-value interval-valued
probability measure]\label{ex:three-dimensional-three-value-1} Given
a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider\emph{ $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, and $\ket{\ps'}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{2})$.
Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'}) & = & \imposs\textrm{ ,}\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'}) & = & \necess\textrm{ ,}\\
\bar{\mu}(P) & = & \unknown\textrm{, otherwise. }
\end{eqnarray*}
To verify $\bar{\mu}$ is a quantum interval-valued probability measure,
first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
it is sufficient to check 
\[
\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)
\]
for orthogonal $\ket{\psi_{0}}$ and $\ket{\psi_{1}}$. This equation
always holds because we always have $\unknown\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)$.

Next, we need to verify that $\bar{\mu}$ is convex. First, for orthogonal
projections $P_{0}$ and $P_{1}$, equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
implies equation (\ref{eq:QuantumInterval-valuedProbability-Convex}).
Second, when $P_{0}=P_{1}+P_{2}$, equation (\ref{eq:QuantumInterval-valuedProbability-Convex})
holds trivially. Hence, we only need to verify the case which $P_{0}=\proj{\psi_{0}}+\proj{\psi_{2}}$
and $P_{1}=\proj{\psi_{1}}+\proj{\psi_{2}}$, where $\left\{ \ket{\psi_{0}},\ket{\psi_{1}},\ket{\psi_{2}}\right\} $
is an orthonormal basis. Because we have 
\begin{eqnarray*}
\bar{\mu}\left(P_{0}\vee P_{1}\right) & = & \bar{\mu}\left(\mathbb{1}\right)=\necess\\
\bar{\mu}\left(P_{0}P_{1}\right) & = & \bar{\mu}\left(\proj{\psi_{2}}\right)\subseteq\unknown
\end{eqnarray*}
and $\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$ is
either $\necess+\unknown$ or $\unknown+\unknown$. Therefore, we
have $\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$.

Finally, we will prove that $\bar{\mu}$ cannot correspond to any
quantum probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
We must have 
\begin{equation}
\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
\end{equation}
By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=0}^{N-1}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\sum_{j=0}^{N-1}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\sum_{j=0}^{N-1}q_{j}=1$ and $q_{j}>0$. However, no pure
state~$\ket{\phi}$ satisfies $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$
so that we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability
measure~$\mu$.\qed\end{example}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\newpage{}%
\begin{comment}
 \bibliographystyle{plain}
\bibliography{prop}
